Column Comparison

### 2021-03-08 gc_column_comparison.Rmd
conflict

@@

# Create a tibble of peak analysis data
peak_data <-
  tibble(
    sample = sample_names,
    file = path_names,
    data = map(file.path(root, file), read_chromeleon_export_peaks),
    injection_details = map(data, "injection_details"),
    peak_analysis = map(data, "peak_analysis")
  ) %>% select(-data)
```

>>>>

# Load Data

@@

# Create a tibble of peak analysis data
peak_data <-
  tibble(
    sample = sample_names,
    file = path_names,
    data = map(file.path(root, file), read_chromeleon_export_peaks),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)
```
